---
title: "Lab 04 Not Team 1"
author: "David Orozco, Arie del Valle, Ethan Schacht, Ryan Tate"
date: "February 8, 2019"
output: html_document
---

```{r , include =FALSE}
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`)
babies <- na.omit(babies)
```

### David's Graph
****
```{r, echo=FALSE}

ggplot(data = babies, mapping = aes(x = bwtoz)) +
  
  geom_density(size = 1) +
  facet_grid(. ~ Premature)+
  ggtitle("Weight Distribution for Premature Babies",subtitle = " 1 = premature, 0 = not premature NA = no answer")

```

* I used geom_density to show the distribution of birht wieght in ounces. I used facet command to show differences in the distribution based on whether or not the baby was premature. ( 1 is born before gestational age of 270, 0 is after 270)

* The mean of the distribution for birth weight of premature babies (~100) is the smallest of the three distributions. 

### Arie's Graph
****
```{r, echo=FALSE, error=FALSE, warning=FALSE}
ggplot(data = babies)+
  geom_jitter(mapping = aes(x = mage, y = bwtoz))+
  ggtitle("Mothers age vs. Birth weight")+
  xlab("Mother's Age")+
  ylab("Birth Wegiht")

```

* I created this plot using geom_jitter.I set x = mother's age and y = birth weight in aesthetic. I usd ggtitle, xlab, and ylab to label all axis and the graph.

* From this graph I found that between age's 20-30, the birth weight is more conssitant. Then, after age 30, the graph shows that birth weight is less conssisent.

### Ethan's Graph
****

```{r, echo=FALSE, error=FALSE, warning=FALSE}
ggplot(data = babies, mapping = aes(x = mpregwt, y = bwtoz), color = "green") +
  geom_point(color = "red", shape = 8) +
  geom_smooth(se = FALSE, method = "lm", color = "black") +
  facet_wrap(~smoke, nrow = 2) +
  xlab("Mother's Weight Before Pregnancy (Pounds)") +
  ylab("Baby's Birth Weight (Ounces)") +
  ggtitle("Mother's Weight vs Baby's Weight by Smoking Freq.", subtitle = "0 = never smokes; 1 = smokes now; NA = no answer")
```

* I created this graph using geom_point and geom_smooth to plot mothers' weights before pregnancy vs babys' birth weights.  I also used facets to separate this correlation by smoking habits to see if smoking affected the correlation between the two weights.  I used xlab, ylab, ggtitle, subtitle, and non-default colors and shapes to enhance my graph's aesthetic appeal.

* I found that there is a minor positive correlation between mothers' pre-pregnancy weights and babys' birth weights.  However, whether or not the mom never smokes or smokes now has no affect on this correlation.

### Ryan's Graph
****

```{r, echo=FALSE, error=FALSE, warning=FALSE}
ggplot(data = babies) +
  geom_histogram(mapping = aes(x = Premature, fill = smoke), binwidth = 0.5) +
  facet_wrap(~smoke)
```

  * I created this graph with geom_histogram to plot the amount of premature babies born for mother's who smoked and mothers who did not smoke during pregnancy.

  * I found that there were born premature babies born from mothers who did not smoke than mothers who did smoke. This could be very misleading though as the number mothers who did not smoke during pregnancy is probably much larger than mothers who did smoke.
  
****
###Team Plot #1
****

```{r, echo=FALSE, error=FALSE, warning=FALSE}
ggplot(data = babies, mapping = aes(x = gestation, y = bwtoz)) +
  geom_point(color = "green") +
  geom_smooth(se = FALSE, method = "lm") +
  facet_wrap(~smoke) +
  xlab("Gestational Age (Days)") +
  ylab("Birth Weight (Ounces)") +
  ggtitle("Gestational Age vs. Birth Weight for 1038 Babies", subtitle = "0 = Mom Doesn't Smoke; 1 = Mom Smokes")
```

