---
title: "Lab 04 Dave"
author: "David Orozco, Arie del Valle, Ethan Schacht, Ryan Tate"
date: "February 8, 2019"
output: html_document
---

```{r , include =FALSE}
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`)
```

### David's Graph
****
```{r, echo=FALSE}

ggplot(data = babies, mapping = aes(x = bwtoz)) +
  
  geom_density(size = 1) +
  facet_grid(. ~ Premature)+
  ggtitle("Weight Distribution for Premature Babies",subtitle = " 1 = premature, 0 = not premature NA = no answer")

```

* I used geom_density to show the distribution of birht wieght in ounces. I used facet command to show differences in the distribution based on whether or not the baby was premature. ( 1 is born before gestational age of 270, 0 is after 270)

* The mean of the distribution for birth weight of premature babies (~100) is the smallest of the three distributions. 

### Arie's Graph
****
```{r, echo=FALSE, error=FALSE, warning=FALSE}
ggplot(data = babies)+
  geom_jitter(mapping = aes(x = mage, y = bwtoz))+
  ggtitle("Mothers age vs. Birth weight")+
  xlab("Mother's Age")+
  ylab("Birth Wegiht")

```

* I created this plot using geom_jitter.I set x = mother's age and y = birth weight in aesthetic. I usd ggtitle, xlab, and ylab to label all axis and the graph.

* From this graph I found that between age's 20-30, the birth weight is more conssitant. Then, after age 30, the graph shows that birth weight is less conssisent.


